Microlensing as a possible probe of event-horizon structure in quasars

### 2016-03-14 paper1/ms.tex
Title change
Changed figure 2

\title{Probing the internal structures of quasars using microlensing events}

\author[Tomozeiu et al]{Mihai Tomozeiu\thanks{mihai@physik.uzh.ch},$^{1,2}$ 
Irshad Mohammed,$^{1,2,3}$ 
Manuel Rabold,$^{1,2}$
Prasenjit Saha,$^{1,2}$  
\newauthor
and Joachim Wambsganss$^4$\\
$^1${Physik-Institut, University of Zurich, Winterthurerstrasse 190,
  8057 Zurich, Switzerland} \\
$^2${Institute for Computational Science, University of Zurich,
  Winterthurerstrasse 190, 8057 Zurich, Switzerland} \\
$^3${Theoretical Astrophysics Group, Fermi National Accelerator Laboratory, Batavia, IL 60510, USA}\\
$^4${Zentrum f\"ur Astronomie der Universit\"at Heidelberg,
  M\"onchhofstrasse 12--14, 69120 Heidelberg, Germany}
}

@@

>>>>

\title{Microlensing as a possible probe of event-horizon structure in quasars}
\author[Tomozeiu et al]{Mihai Tomozeiu\thanks{mihai@physik.uzh.ch},$^{1,2}$ 
Irshad Mohammed,$^{1,2,3}$ 
Manuel Rabold,$^{1,2}$
Prasenjit Saha,$^{1,2}$  
\newauthor
and Joachim Wambsganss$^4$\\
$^1${Physik-Institut, University of Zurich, Winterthurerstrasse 190,
  8057 Zurich, Switzerland} \\
$^2${Institute for Computational Science, University of Zurich,
  Winterthurerstrasse 190, 8057 Zurich, Switzerland} \\
$^3${Theoretical Astrophysics Group, Fermi National Accelerator Laboratory, Batavia, IL 60510, USA}\\
$^4${Zentrum f\"ur Astronomie der Universit\"at Heidelberg,
  M\"onchhofstrasse 12--14, 69120 Heidelberg, Germany}
}

@@

\textit{Author contributions}\\
Prasenjit Saha provided the original idea and plan for the research project as well as multiple contributions to the analysis.
 Mihai Tomozeiu simulated and studied the ideal behaviour of the microlensing lightcurves for the different source profiles discussed.
 Joachim Wambsganss provided the numerical code used by Manuel Rabold to create the magnification map and corresponding lighcurves 
used in the MCMC analysis performed by Irshad Mohammed in the last part of the presented work.
